Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-03 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#2}

\noindent \emph{This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors: } \\

\noindent (1) \emph{The ANN and ELM (extreme learning machine) should be added into the experiments; }

\begin{verbatim}
We have added the results of ANN (MLP) and ELM to all tables 
accordingly. A description of both approaches have been also 
added to subsection 2.1.
\end{verbatim}

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology by including a flowchart (see Figure 1 
at page 6).
\end{verbatim}

~\\
\noindent (4) \emph{In Section 5, parameter settings of M5P, kNN and RF also should be shown. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
section 5, including the parameter settings of M5P, kNN and RF 
methods.
\end{verbatim}
